A Certified Interpreter for the List Machine Benchmark

### 2020-06-17 papers/SBLP2020/paper.tex
Small updates

Using the previously defined type syntax and its subtyping relation, we can
define the typing rules for the list machine. Following common practice, we
let meta-variable $\Gamma$ denote an environment between variable names and
its type. Notation $\{\}$ denote an empty environment and $v : \tau , \Gamma'$
denote the operation of including a new entry for variable $v$ with type $\tau$.
Subtyping is extended to contexts as follows.
\[
\begin{array}{cc}
  \inference{}
            {\Gamma \subset_{env} \{\}}[b1]
  &
  \inference{\Gamma_1 = (v : \tau') , \Gamma' & \tau' \subset \tau & \Gamma' \subset_{env} \Gamma_2}
            {\Gamma_1 \subset_{env} v : \tau , \Gamma_2}
            [b2]
\end{array}
\]
Variable $\Pi$ denote \emph{program typings}, i.e. finite mappings between labels and typing contexts $\Gamma$.
Notation $\Pi(l) = \Gamma$ denotes that $\Gamma$ stores the types of variables on the entry point of the block
labeled by $l$.

>>>>

Using the previously defined type syntax and its subtyping relation, we can
define the typing rules for the list machine. Following common practice, we
let meta-variable $\Gamma$ denote an environment between variable names and
its type. Notation $\{\}$ denote an empty environment and $v : \tau , \Gamma'$
denote the operation of including a new entry for variable $v$ with type $\tau$.
Subtyping is extended to contexts as follows.
\[
\begin{array}{cc}
  \inference{}
            {\Gamma \subset_{env} \{\}}[b1]
  &
  \inference{\tau' \subset \tau & \Gamma' \subset_{env} \Gamma_2}
            {v : \tau' , \Gamma' \subset_{env} v : \tau , \Gamma_2}
            [b2]
\end{array}
\]
Variable $\Pi$ denote \emph{program typings}, i.e. finite mappings between labels and typing contexts $\Gamma$,
where notation $\Pi(l) = \Gamma$ denotes that $\Gamma$ stores the types of variables on the entry point of the block
labeled by $l$.
